---
title: "Understanding State Preferences With Text As Data: Introducing the UN General Debate Corpus"
author:
- affiliation: Dublin City University
  email: alex.baturo@dcu.ie
  name: Alexander Baturo
- affiliation: University of Birmingham
  email: n.dasandi@bham.ac.uk
  name: Niheer Dasandi
- affiliation: University of Essex
  email: slava.mikhaylov@gmail.com
  name: Slava Mikhaylov
date: 28 January 2017
output:
  html_notebook:
    toc: yes
  html_document: default
  pdf_document: default
  toc: yes
  word_document: default
#biblio-style: apsr
#bibliography: un.bib
thanks: Authors' names are listed in alphabetical order. Authors have contributed equally to all work.
abstract: Every year at the United Nations, member states deliver statements during the General Debate discussing major issues in world politics. These speeches provide invaluable information on governments' perspectives and preferences on a wide range of issues, but have largely been overlooked in the study of international politics. This paper introduces a new dataset consisting of over 7,300 country statements from 1970--2014. We demonstrate how the UN General Debate Corpus (UNGDC) can be used to derive country positions on different policy dimensions using text analytic methods. The paper provides applications of these estimates, demonstrating the contribution the UNGDC can make to the study of international politics.
---


##Reading in UNGDC


```{r}
#Loading packages and data
library(readtext)
library(quanteda)
library(dplyr)
library(stringr)
library(ggplot2)
library(rworldmap)
library(RColorBrewer)
library(classInt)
library(vegan)
library(boot)
library(haven)
library(readxl)
library(texreg)
```


```{r warning=FALSE}

if (!require("readtext")) devtools::install_github("kbenoit/readtext")

#File path to UNGDC unzipped data archive
DATA_DIR <- "~/Dropbox/Research/UN Data/" 

#Reading in text files
ungd_files <- readtext(paste0(DATA_DIR, "Converted sessions/*"), 
                                 docvarsfrom = "filenames", 
                                 dvsep="_", 
                                 docvarnames = c("Country", "Session", "Year"))

if (!require("quanteda")) devtools::install_github("kbenoit/quanteda")

#Creating corpus
ungd_corpus <- corpus(ungd_files, text_field = "text") 

#Creating corpus for 2014, for Wordscore example below
ungdc.2014 <- corpus_subset(ungd_corpus, Year==2014)

```


##UNGDC corpus summary

```{r}

summarise(group_by(summary(ungd_corpus, n = 7314, verbose = FALSE),Year),
                           mean(Types),mean(Tokens),
                           mean(Sentences),min(Sentences),max(Sentences))

```

##Summary of speakers

As discussed in the text we categorize speakers by:

1) heads of state or government (e.g. presidents, prime ministers, kings); 
2) vice-presidents, deputy prime ministers, and foreign ministers; 
3) country representative at the UN.

```{r}
#Reading in Excel spreadsheet with speakers information
posts <- read_excel("posts_of_speakers.xlsx")
table <- table(posts$Post)
table
```


```{r}
#Proportions by category
prop.table(table)
```


##Tokenizing documents

```{r}
#Tokenization and basic pre-processing
tok <- tokens(ungd_corpus, what = "word",
              removePunct = TRUE,
              removeSymbols = TRUE,
              removeNumbers = TRUE,
              removeTwitter = TRUE,
              removeURL = TRUE,
              removeHyphens = TRUE,
              verbose = TRUE)
```


##Creating document feature matrix


```{r dfm}
#DFM creation from tokens, removing stopwords, and stemming.
dfm <- dfm(tok, 
           tolower = TRUE,
           remove=stopwords("SMART"),
           stem=TRUE, 
           verbose = TRUE)

#Showing 100 most frequrent tokens in DFM
topfeatures(dfm, n = 100)

```


##Removing some features

As part of converting original transcripts held by UN library to digital, machine-readable format, we had to OCR documents before 1994. That introduced several tokens that were compounded with digits, punctuation and other OCR errors. We are cleaning it up here with brute force purging of DFM.

```{r}
#Removing any digits. `dfm` picks up any separated digits, not digits that are part of tokens.
dfm.m <- dfm_select(dfm, '[\\d-]',  selection = "remove", 
                    valuetype="regex", verbose = TRUE)


#Removing any punctuation. `dfm` picks up any punctuation unless it's part of a token.
dfm.m <- dfm_select(dfm.m, "[[:punct:]]",  selection = "remove", 
                    valuetype="regex", verbose = TRUE)


#Removing any tokens less than four characters.
dfm.m <- dfm_select(dfm.m, '^.{1,3}$',  selection = "remove", 
                    valuetype="regex", verbose = TRUE)

#100 least frequent terms
topfeatures(dfm.m, n = 100, decreasing = FALSE)
```

##Trimming DFM

Some of the least frequent terms above are due to OCR and text digitization errors. In addition, we want to reduce dimensionality of DFM for subsequent computation.

```{r}
#Dropping words that appear less than 5 times and in less than 3 documents.
dfm.trim <- dfm_trim(dfm.m, min_count = 5, min_docfreq = 3)

#100 least frequent terms in trimmed DFM
topfeatures(dfm.trim, n = 100, decreasing = FALSE)

#Level of sparsity of trimmed DFM
sparsity(dfm.trim)

#Number of features in trimmed DFM
nfeature(dfm.trim)
```



##Wordscore estimates

In the Wordscore example we focus only on subset of the UNGDC corpus (`ungdc.2014`). 

```{r}
#Reference scores
refscores <- rep(NA,nrow(dfm.trim))

refscores[str_detect(rownames(dfm.trim), "RUS")] <- -1
refscores[str_detect(rownames(dfm.trim), "USA")] <- 1

#Wordscore model
ws <- textmodel_wordscores(dfm.trim, refscores, scale="linear", smooth=1)
wordscore <- predict(ws, rescaling="lbg")

#Writing the results into data frame
wordscores.2014 <- data.frame(cbind(docvars(ungdc.2014),
                                       wordscore@textscores$textscore_lbg))

wordscores.2014 <- dplyr::rename(wordscores.2014, wscore = wordscore.textscores.textscore_lbg)
```


##Map with 2014 wordscore results

```{r}
sPDF <- joinCountryData2Map(wordscores.2014,
                            joinCode="ISO3",nameJoinColumn="Country")

#Setting up class intervals for continuous variable
classInt <- classIntervals(sPDF$wscore,
                           style="kmeans")

catMethod=classInt$brks

#Selecting diverging palette
colourPalette <- brewer.pal(9,"Blues")
#colourPalette <- brewer.pal(9,"PuOr")

#Drawing the map

mapParams <- mapCountryData(sPDF,nameColumnToPlot="wscore", 
                            #catMethod="pretty", 
                            catMethod=catMethod,
                            mapTitle="USA vs Russia: Wordscore 2014",
                            colourPalette=colourPalette,
                            #oceanCol="lightblue",
                            missingCountryCol="grey", 
                            addLegend="FALSE"
                            #borderCol="black"
)

#adding legend
do.call( addMapLegend, c( mapParams, legendLabels="limits", 
                          labelFontSize=0.7,legendShrink=0.7,
                          legendMar=4, legendWidth=0.6))


```

## Correspondence Analysis

```{r}
#Note: takes about 2h on full corpus, on MacBook Pro (3 GHz, 16GB RAM)
system.time(ca <- cca(dfm.trim))
ca
```


```{r}
#Extracting CA scores on first 10 dimensions
scores <- as.data.frame(scores(ca,choices=c(1:10), display="wa", scaling=1))

#Adding docvars
ca.scores <- data.frame(cbind(docvars(ungd_corpus), scores))

```



##CA plots


```{r}
#Dimension 1
ggplot(data=subset(ca.scores,Country=="USA" | Country=="RUS"), 
            aes(x=Year, y=CA1, group=Country, colour=Country)) +
  theme_bw() +
  ggtitle("USA and Russia") + ylab("CA Dimension 1")+
  theme(plot.title = element_text(lineheight=.8, face="bold", size=15),
        axis.title.x = element_text(face="bold", size=11),
        axis.title.y = element_text(face="bold", size=11),
        axis.text.x  = element_text(angle=90, vjust=0.5, size=8)) +
  scale_y_continuous() +
  scale_x_continuous(breaks = seq(1970,2014,2)) +
  geom_smooth(se = FALSE) + 
  geom_point(aes(shape=Country))
  

#ggsave("RusUSA-CA1.pdf")


```




```{r}
#Dimension 1
ggplot(data=subset(ca.scores,Country=="USA" | Country=="GBR"), 
            aes(x=Year, y=CA1, group=Country, colour=Country)) +
  theme_bw() +
  ggtitle("USA and UK") + ylab("CA Dimension 1")+
  theme(plot.title = element_text(lineheight=.8, face="bold", size=15),
        axis.title.x = element_text(face="bold", size=11),
        axis.title.y = element_text(face="bold", size=11),
        axis.text.x  = element_text(angle=90, vjust=0.5, size=8)) +
  scale_y_continuous() +
  scale_x_continuous(breaks = seq(1970,2014,2)) +
  geom_smooth(se = FALSE) + 
  geom_point(aes(shape=Country))
  

#ggsave("GBRUSA-CA1.pdf")


```




```{r}
#Dimension 2
ggplot(data=subset(ca.scores,Country=="USA" | Country=="RUS"), 
            aes(x=Year, y=CA2, group=Country, colour=Country)) +
  theme_bw() +
  ggtitle("USA and Russia") + ylab("CA Dimension 2")+
  theme(plot.title = element_text(lineheight=.8, face="bold", size=15),
        axis.title.x = element_text(face="bold", size=11),
        axis.title.y = element_text(face="bold", size=11),
        axis.text.x  = element_text(angle=90, vjust=0.5, size=8)) +
  scale_y_continuous() +
  scale_x_continuous(breaks = seq(1970,2014,2)) +
  geom_smooth(se = FALSE) + 
  geom_point(aes(shape=Country))
  

#ggsave("RusUSA-CA2.pdf")


```





```{r}
#Dimension 2
ggplot(data=subset(ca.scores,Country=="USA" | Country=="GBR"), 
            aes(x=Year, y=CA2, group=Country, colour=Country)) +
  theme_bw() +
  ggtitle("USA and UK") + ylab("CA Dimension 2")+
  theme(plot.title = element_text(lineheight=.8, face="bold", size=15),
        axis.title.x = element_text(face="bold", size=11),
        axis.title.y = element_text(face="bold", size=11),
        axis.text.x  = element_text(angle=90, vjust=0.5, size=8)) +
  scale_y_continuous() +
  scale_x_continuous(breaks = seq(1970,2014,2)) +
  geom_smooth(se = FALSE) + 
  geom_point(aes(shape=Country))
  

#ggsave("GBRUSA-CA2.pdf")


```



##Empirical example: Extending a model in Kelley (2007)


```{r}
#Replication Stata file provided by Judith Kelley
replication <- read_dta("Replication.dta")

replication <- rename(replication, Country=abbrev) 

#merging replication file with CA estimates
combined.data <- merge(replication, subset(ca.scores,Year==2002), by="Country")
dim(combined.data)

#Keeping only complete data for subsequent estimations. CV.GLM requires complete cases.
combined.data <- na.omit(combined.data)
#67 observations dropped
dim(combined.data)

```



###Estimating a logit model
```{r}
#Original model
glm.fit <- glm(coop ~ polityDEM + LikeMinded + Physint + lngdp2004 + gsp + 
                 cut + IraqSupport + dummyRatif + RuleOfLaw, 
               data=combined.data,
               family = binomial)

summary(glm.fit)

```


###Using cross-validation to calculate the number of dimensions to include

Given that each CA dimension is orthogonal to each other, we simply add dimensions sequentially. This is driven by theoretical logic whether one, two, or $k$ CA dimensions should be used in the GLM model above. We search up to ten CA dimensions. And implement a version of leave-one-out cross-validation. This is a very simple search through specifications for illustrative purposes only.



```{r}

set.seed(2)


cv.error <- rep(0,10)

glm.fit.1 <- glm(coop ~ polityDEM + LikeMinded + Physint + lngdp2004 + gsp + 
                   cut + IraqSupport + dummyRatif + RuleOfLaw +
                   CA1, 
                 data=combined.data,
                 family = binomial)

summary(glm.fit.1)

cv.error[1] <- cv.glm(combined.data, glm.fit.1)$delta[1]

#####
glm.fit.2 <- glm(coop ~ polityDEM + LikeMinded + Physint + lngdp2004 + gsp + 
                   cut + IraqSupport + dummyRatif + RuleOfLaw +
                   CA1 + CA2, 
                 data=combined.data,
                 family = binomial)

summary(glm.fit.2)

cv.error[2] <- cv.glm(combined.data, glm.fit.2)$delta[1]

######

glm.fit.3 <- glm(coop ~ polityDEM + LikeMinded + Physint + lngdp2004 + gsp + 
                   cut + IraqSupport + dummyRatif + RuleOfLaw +
                   CA1 + CA2 + CA3, 
                 data=combined.data,
                 family = binomial)

summary(glm.fit.3)

cv.error[3] <- cv.glm(combined.data, glm.fit.3)$delta[1]

######

glm.fit.4 <- glm(coop ~ polityDEM + LikeMinded + Physint + lngdp2004 + gsp + 
                   cut + IraqSupport + dummyRatif + RuleOfLaw +
                   CA1 + CA2 + CA3 + CA4, 
                 data=combined.data,
                 family = binomial)

summary(glm.fit.4)

cv.error[4] <- cv.glm(combined.data, glm.fit.4)$delta[1]


######

glm.fit.5 <- glm(coop ~ polityDEM + LikeMinded + Physint + lngdp2004 + gsp + 
                   cut + IraqSupport + dummyRatif + RuleOfLaw +
                   CA1 + CA2 + CA3 + CA4 + CA5, 
                 data=combined.data,
                 family = binomial)

summary(glm.fit.5)

cv.error[5] <- cv.glm(combined.data, glm.fit.5)$delta[1]

######

glm.fit.6 <- glm(coop ~ polityDEM + LikeMinded + Physint + lngdp2004 + gsp + 
                   cut + IraqSupport + dummyRatif + RuleOfLaw +
                   CA1 + CA2 + CA3 + CA4 + CA5 + CA6, 
                 data=combined.data,
                 family = binomial)

summary(glm.fit.6)

cv.error[6] <- cv.glm(combined.data, glm.fit.6)$delta[1]


######

glm.fit.7 <- glm(coop ~ polityDEM + LikeMinded + Physint + lngdp2004 + gsp + 
                   cut + IraqSupport + dummyRatif + RuleOfLaw +
                   CA1 + CA2 + CA3 + CA4 + CA5 + CA6 + CA7, 
                 data=combined.data,
                 family = binomial)

summary(glm.fit.7)

cv.error[7] <- cv.glm(combined.data, glm.fit.7)$delta[1]

######

glm.fit.8 <- glm(coop ~ polityDEM + LikeMinded + Physint + lngdp2004 + gsp + 
                   cut + IraqSupport + dummyRatif + RuleOfLaw +
                   CA1 + CA2 + CA3 + CA4 + CA5 + CA6 + CA7 + CA8, 
                 data=combined.data,
                 family = binomial)

summary(glm.fit.8)

cv.error[8] <- cv.glm(combined.data, glm.fit.8)$delta[1]

######

glm.fit.9 <- glm(coop ~ polityDEM + LikeMinded + Physint + lngdp2004 + gsp + 
                   cut + IraqSupport + dummyRatif + RuleOfLaw +
                   CA1 + CA2 + CA3 + CA4 + CA5 + CA6 + CA7 + CA8 + CA9, 
                 data=combined.data,
                 family = binomial)

summary(glm.fit.9)

cv.error[9] <- cv.glm(combined.data, glm.fit.9)$delta[1]

######

glm.fit.10 <- glm(coop ~ polityDEM + LikeMinded + Physint + lngdp2004 + gsp + 
                    cut + IraqSupport + dummyRatif + RuleOfLaw +
                    CA1 + CA2 + CA3 + CA4 + CA5 + CA6 + CA7 + CA8 + CA9 + CA10, 
                  data=combined.data,
                  family = binomial)

summary(glm.fit.10)

cv.error[10] <- cv.glm(combined.data, glm.fit.10)$delta[1]

cv.error


error <- as.data.frame(cv.error)

```

###Plotting cross-validation error

We are selecting the number of CA dimensions based on the lowest CV error. Here it is the model with three first CA dimensions.

```{r}
ggplot(data=error, aes(x=row(error), y=cv.error)) +
  geom_point(color='blue', size=1) +
  theme_bw() +
 scale_x_continuous(breaks=seq(0,10,1), name = "Number of dimensions") +
  ylab("CV error") +
  ggtitle("LOOCV results")

#ggsave("cv.pdf")

```



###Graph of results

Plotting the results of GLM model with three CA dimensions included in the model.

```{r}

plotreg(glm.fit.3, custom.note = "",
                custom.coef.names = c("intercept", "Polity", "Allies", "HR", 
                           "GDP", "GSP status", "Military aid", "Iraq war", 
                           "ICC ratification", "Rule of law", "CA1", "CA2", "CA3"),
                custom.model.names = "Bilateral nonsurrender agreements with US")

```


###Insights into CA3

We use `goodness` function from package `vegan` to extract the terms that account for most of variation (inertia) on a dimension (axis). 

```{r}
ca3 <- as.data.frame(goodness(ca, model =  "CA", choices=3))

ca3$words <- rownames(ca3)

```


We can visualize the top loading words using a simple wordcloud.

```{r}
wordcloud::wordcloud(ca3$words,ca3$CA3,
                     max.words = 100,
                     random.order = FALSE,
                     rot.per = .3,
                     scale = c(3, .1), 
                     colors = brewer.pal(6, "Blues"))

```


##Session Information
For replication purposes, we're providing session information.
```{r}
sessionInfo()
```

